---
title: "Project 2 Solutions"
output:
  pdf_document: default
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## (Abhimanyu Agarwal)

## Collaborators: N/A
## TA help: 
## 1) Hilda Ibriga - Question 4 and 5, Helped me understanding and applying concepts in R.
## 2) Evan Li, Cross-checked my knitted pdf to enhance result reporting professionally. 
## Online resources used: N/A 

### Question 1
```{r}
#Loads into dataframe called myDF
myDF<-read.csv("/class/datamine/data/disney/metadata.csv")

#Prints the first 1 line using head() just to see 
head(myDF, n = 1) 

#Note: TA suggested to print a few lines just because there are so many columns to print otherwise. 
```

### Question 2
```{r}
#Given code in project 
our_vec <- myDF$WDWMAXTEMP

#Prints the first value
firstval <- our_vec[1]
head(firstval)
#Printed value is: 73.02

#Prints the 50th value
fiftyval <- our_vec[50]
head(fiftyval)
#Printed value is: 51.24

#Type of a vector
typeof(our_vec)
#Type is "double"
```

### Question 3
```{r}
#First 50 values 
first50 <- head(our_vec, n = 50)
head(first50)
#Prints values of first 50 elements

#Last 50 values
last50 <- tail(our_vec, n = 50)
head(last50)
#Prints the values of last 50 elements

#Adding the two element vectors  
mix <- first50 + last50
head(mix)
#Prints the values of after performing addition 
```

### Question 4
```{r}
#Stores the temperature values greater or equal to 80. Since our_vec is already defined 
hot <- our_vec[our_vec >= 80]
head(hot)
#Prints some values
```

```{r}
#Tells us how many elements are in hot (vector)
length(hot)
```

```{r}
#Sum of hot and first50
result <- hot + first50
```

Explanantion : We get an error message that is because of the length of the two vectors is not the same. When we perform addition it adds the vectors element by element which results in a vector. Since the lengths of the two vectors here are different, we get a warning message as seen. R performs recycling on the shorter one by making the two vectors equal. This addition also results in a vector. 
```{r}
#prints result 
head(result)
```

### Question 5
```{r}
#Plotting the values captured by the vector
plot(our_vec, main='Max temperature Range (Degrees (F))', col='orange')
```

### Question 6
```{r}
#Favorite graph would be the second one. The code is below as given:
library(ggplot2)
library(tidyverse)
summary_temperatures <- myDF %>%
  select(MONTHOFYEAR,WDWMAXTEMP:WDWMEANTEMP) %>%
  group_by(MONTHOFYEAR) %>%
  summarise_all(mean, na.rm=T)
ggplot(summary_temperatures, aes(x=MONTHOFYEAR)) +
  geom_ribbon(aes(ymin = WDWMINTEMP, ymax = WDWMAXTEMP), fill = "#ceb888", alpha=.5) +
  geom_line(aes(y = WDWMEANTEMP), col="#5D8AA8") +
  geom_point(aes(y = WDWMEANTEMP), pch=21,fill = "#5D8AA8", size=2) +
  theme_classic() +
  labs(x = 'Month', y = 'Temperature', title = 'Average temperature range' ) +
  scale_x_continuous(breaks=1:12, labels=month.abb)
```

1.    It is my favorite graphic because it is extremely detailed making it reader friendly
      open to interpretation and does not show absurd variations. 
      It discusses the topic of Average Temperature Range. 
      Moreover, this plot does not convey all information properly.
2.    It could be improvised by adding a legend, smoothing the variation 
      could give a better sense of the Temperature Vs Month variation. 
3.    A fascinating aspect that attracted my attention was the bell 
      shape of the plot with the peak being at approximately 80 Degrees(F). 
      
Submitting deliverables: project02.RMD, project02.R and project02.pdf

## Pledge

By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
