---
title: "Project 8 Solutions"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## (Abhimanyu Agarwal)

## Collaborators: N/A
## TA help: 
## 1) Melissa : Helped me go through Question 4 and 5. 
## Online resources used: N/A 

### Question 1
```{r}
#Loads into two distinct dataframes using read.csv()
books <- read.csv("/class/datamine/data/goodreads/csv/goodreads_books.csv")
authors <- read.csv("/class/datamine/data/goodreads/csv/goodreads_book_authors.csv")

strip_punctuation <- function(myColumn) {
  # Use regular expressions to identify punctuation.
  # Replace identified punctuation with an empty string ''.
  
  desc_no_punc <- gsub('[[:punct:]]+', '', myColumn)
  
  # Return the result
  return(desc_no_punc)
}

books$description <- strip_punctuation(books$description)
head(books$description)
#The function has one argument. It is called "mycolumn". The name of the function is string_punctation. 
```

### Question 2
```{r}
#Initialize the test string 
test_string <- "This is  a test string  with no punctuation"

#Now we split the string into individual components using strsplit 
strsplit(test_string, c(" "))

#No, it is not accurate as it takes into account several other punctuations. 
#This affects the net result as to how the split turns out to be. 
```

### Question 3
```{r}
unlist(strsplit(c(test_string)," "))
sum(unlist(strsplit(test_string, " ") [[1]] != ""))

#It is an alternative way of doing it 
#Uses the length instead both account 8
length(which(unlist(strsplit(test_string, " ") [[1]] != "")))
#Prints out the number of words
```

### Question 4
```{r}
#Count the number of words in the specified description row & column
count_words <- function(description)
  {
  aux <- gsub('[[:punct:]]+','', description)
  
  # split the sentence by space and remove extra spaces
  result <- sum(unlist(strsplit(aux, " ")) != "")
  
  return(result)
  }
count_words(books$description[2])
#Prints out the result 
```

###Question 5
```{r}
#Function takes in one argument and returns split based on first name, middle name and last. The argument is the complete name.
myfunction<- function(names) 
{
  return (unlist(strsplit(names, c(" "))))
}
head(authors$name)
head(myfunction(authors$name))
tail(myfunction(authors$name))
```

Submitting deliverables: project08.RMD, project08.R and project08.pdf

## Pledge
By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
