---
output:
  pdf_document: default
  html_document: default
---

---
title: "Project 10 Solutions"
output:
  pdf_document: default
  latex_engine: xelatex
  html_document:
    df_print: paged
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

### Question 1
library(imager)
library(knitr)
opts_chunk$set(comment = NA)
```

## (Abhimanyu Agarwal)

## Collaborators: N/A
## TA help: 
## 1) Melissa : Helped me go through Question 4 and 5. 
## Online resources used: N/A 

### Question 1
```{r}
users <- read.csv("/class/datamine/data/okcupid/filtered/users.csv")
questions <- read.csv("/class/datamine/data/okcupid/filtered/questions.csv", sep=";")

#head(questions)
#The questions dataframe stores data regarding the various questions and available options. 
#head(users)
#The user dataframe has just captures various answers.  

```

### Question 2
```{r}
grep("google", questions$text, ignore.case = T)
questions$text[grep("google", questions$text, ignore.case = T)]
# Question is : "Do you Google someone before a first date?"
```

### Question 3
```{r}
questions[grep("google", questions$text, ignore.case = T),]

#Table 
prop.table(table(users$q170849, useNA = "always"))
#Ratio is ~37% No's and 20% acceptances 

#Gives percentage based on Man or Woman 
tapply(users$q170849, users$gender2, function(x) {prop.table(table(users$q170849, useNA = "always"))})
#The ratio is same for each gender. They are ~37% No's and only ~20% yes

#Gives percetange based on Gender Orientation 
tapply(users$q170849, users$gender_orientation, function(x) {prop.table(table(users$q170849, useNA = "always"))})
#The ratio is same for each gender orientation. They are ~37% No's and only ~20% yes
```

### Question 4
```{r}
count_words <- function(my_text) {
    my_split_text <- unlist(strsplit(my_text, " "))
    
    return(length(my_split_text[my_split_text!=""]))
}

#Making the new column question_length which is put into questions 
questions$question_length <- sapply(questions$text, count_words)

```

###Question 5
```{r}
number_of_options <- function(myDF) 
{
  table(apply(as.matrix(myDF[ ,3:6]), 1, function(x) {sum(!(x==""))}))
}

#Gives options based on the keyword list 
keywordlist <- split(questions, questions$Keywords)
sapply(keywordlist, number_of_options)
```

###Question 6
```{r}
par(mfrow=c(2,3))
sapply(tapply(users$q170849, users$gender2, function(x) {prop.table(table(users$q170849, useNA = "always"))}), pie)
#Was just curious to see how the plot comes to be. Essentially i think visual representations are extremely important 
#as it gives a sense of proportions effectively 
```

Submitting deliverable: project10.RMD, project10.R and project10.pdf

## Pledge
By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
