---
title: "Project 3 Solutions"
output:
  pdf_document: default
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## (Abhimanyu Agarwal)

## Collaborators: N/A
## TA help: 
## 1) Melissa: Helped on understanding the which() function. 
## Online resources used: N/A 

### Question 1
```{r}
#Loads into dataframe called "splash_mountain" using read.csv()
splash_mountain <-read.csv("/class/datamine/data/disney/splash_mountain.csv")

#Columns/features in the dataset 
str(splash_mountain)

#Either works, just out of curiosity i used both to see the difference in the information being conveyed.

#Returns the two values, the first value = rows and second value = columns:
dim(splash_mountain)
```

### Question 2
```{r}
#Code to find SPOTSMIN 
head(splash_mountain$SPOSTMIN)

#Code to find SACTMIN
head(splash_mountain$SACTMIN)

#Code to estimate the mean by removing NA values 
mean(splash_mountain$SPOSTMIN, na.rm=TRUE)
#Obtained mean is: -71.70373

#Code to estimate the standard deviation by removing NA values 
sqrt(var(splash_mountain$SPOSTMIN, na.rm=TRUE))
#Obtained Standard deviation is: 328.0586 

#Result explanation here
# The data set column given to us talks about wait time.
# Waiting time expected cannot be negative quantity.
# Mean obtained is negative, which is impossible in reality. 
# Hence we can say that the data set comprises of large negative values 
# or significantly small positive values 
```

### Question 3
```{r}
#Here we are using TRUE's and FALSE's as indexes 
#Code to estimate the mean by removing NA values 
mean(splash_mountain$SPOSTMIN[splash_mountain$SPOSTMIN != -999], na.rm=TRUE)
#Newly obtained mean is: 43.3892

#Code to estimate the standard deviation by removing NA values 
sqrt(var(splash_mountain$SPOSTMIN[splash_mountain$SPOSTMIN != -999], na.rm=TRUE))
#Newly obtained standard deviation is: 31.74894

#Result explanation here
#Yes, this solves the problem. Now that, negative value -999 has been eliminated
#the computed mean is a positive and believable value. Earlier, when the mean 
#was negative, it didn't make sense to have a negative mean for the wait time.
```

### Question 4
```{r}
#Change SPOSTMIN to posted_min_wait time
head(splash_mountain)
colnames(splash_mountain)[which(colnames(splash_mountain)=="SPOSTMIN")] <- "posted_min_wait_time"
#View the name change 
head(splash_mountain)

#Change SACTMIN to actual_wait_time
head(splash_mountain)
colnames(splash_mountain)[which(colnames(splash_mountain)=="SACTMIN")] <- "actual_wait_time" 
#View the name change 
head(splash_mountain)
```

### Question 5
```{r}
#Loading the samedata in a dataframe "df"
myDF <- read.csv("/class/datamine/data/disney/splash_mountain.csv")
head(myDF)

#Now using the cut() functions 
quarter <- cut(as.Date(myDF$date, "%m/%d/%Y"), "quarter")

#Estimating the possible combinations 
nlevels(quarter)
#There are 20 quarters as we can see.

#Using factor() function we put labels like "q1", "q2"...etc 
levels(quarter) <- factor(paste0("q", 1:nlevels(quarter)))

#Now we add a new column called "quarter" 
myDF$quarter<-quarter

#Now we check and observe that there is indeed a new column by the name "quarter"
head(myDF)
tail(myDF)

```

### Question 6
```{r}
#Including the statement 
cat ("I acknowledge that the STAT 19000/29000/39000 1-credit Data Mine seminar will be recorded and posted on Piazza, for participants in this course.")
```      

Submitting deliverables: project03.RMD, project03.R and project03.pdf

## Pledge
By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
