---
title: "Project 5 Solutions"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## (Abhimanyu Agarwal)

## Collaborators: N/A
## TA help: 
## 1) Melissa : Helped me go through Question 3 and 4. 
## Online resources used: N/A 

### Question 1
```{r}
#Loads into dataframe called "accidents" using read.csv() and rbind()
accidents <- rbind(read.csv("/class/datamine/data/fars/1975/ACCIDENT.CSV"),
                   read.csv("/class/datamine/data/fars/1976/ACCIDENT.CSV"),
                   read.csv("/class/datamine/data/fars/1977/ACCIDENT.CSV"),
                   read.csv("/class/datamine/data/fars/1978/ACCIDENT.CSV"),
                   read.csv("/class/datamine/data/fars/1979/ACCIDENT.CSV"),
                   read.csv("/class/datamine/data/fars/1980/ACCIDENT.CSV"),
                   read.csv("/class/datamine/data/fars/1981/ACCIDENT.CSV"))
#Reports the dataframes dimensions 
dim(accidents)

#Adds a new year column that contains the full year
accidents$YEAR <- factor(paste0("19", accidents$YEAR))

#Prints the updated datframe 
head(accidents)

#Displays the output for the unique()
#Basically displays the unique levels/states 
unique(accidents$YEAR)
```

### Question 2
```{r}
table(accidents$DRUNK_DR)
table(accidents$SCH_BUS, useNA = "always")

#Gives you a table to see when is that true, false or N/A  
table((accidents$DRUNK_DR != 0)&(accidents$SCH_BUS == 1), useNA = "always")

#Number of accidents in totality with atleast 1 drunk driver and 1 bus.
length(which((accidents$DRUNK_DR != 0)&(accidents$SCH_BUS == 1)))
#There are 101 accidents with at least 1 drunk driver with a school bus. 

```

### Question 3
```{r}
#Tells how many accidents took place in the given span of time (for each year).
table(accidents$YEAR[(accidents$DRUNK_DR != 0)&(accidents$SCH_BUS == 1)])

#Tells what is maximum amount of accidents. 
max(table(accidents$YEAR[(accidents$DRUNK_DR != 0)&(accidents$SCH_BUS == 1)]))

#Tells which year witnessed maximum amount of accidents.
which.max(table(accidents$YEAR[(accidents$DRUNK_DR != 0)&(accidents$SCH_BUS == 1)]))
#1978 has the maximum number of accidents  
```

### Question 4
```{r}
#Groups the variable/ first argument into categories based on the second argument
#Applies specific mathematical function like variance, sum etc to the grouped data.
tapply(accidents$PERSONS, accidents$DRUNK_DR, mean)

```

###Question 5
```{r}
#Captures the relevant states data into the dataframe "state"
state <- accidents[(accidents$STATE %in% c(17,18,26,39)), ]

#Table t is formulated 
t <- table(state$STATE, state$MONTH)

#Barplot with legend is generated
barplot(t, legend = rownames(t))

#From the bar graph, it can be concluded that the summer months (6 to 9) witness 
#the greatest rise in the number of accidents. As the summer passes a decrease 
#in the incidents can be observed. The increment in the accident numbers can be 
#because of people could be on vacations during the summer or partying with friends.
#With all the hustle, maybe people just arent as attentive as they should be. 

```

Submitting deliverables: project05.RMD, project05.R and project05.pdf

## Pledge
By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
