---
title: "Project 7 Solutions"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## (Abhimanyu Agarwal)

## Collaborators: N/A
## TA help: 
## 1) Melissa : Helped me go through Question 4 and 5. 
## Online resources used: N/A 

### Question 1
```{r}
#Loads into two distinct dataframes using read.csv()
books <- read.csv("/class/datamine/data/goodreads/csv/goodreads_books.csv")
authors <- read.csv("/class/datamine/data/goodreads/csv/goodreads_book_authors.csv")

#Dimension for books dataframe
dim(books)

#Dimension for authors dataframe
dim(authors)


```

### Question 2
```{r}
#Using the cut function to break into 4 categories 
book_size <- cut(books$num_pages, breaks = c(0,250,500,1000,Inf), labels = c("small", "medium", "large", "huge"), include.lowest=T)
table(book_size)
```

### Question 3
```{r}
#calculate the mean average_rating
tapply(books$average_rating, book_size, mean, na.rm = T)

#calculate the mean text_reviews_count
tapply(books$text_reviews_count, book_size, mean, na.rm = T)

#calculate the mean publication_year
tapply(books$publication_year, book_size, mean, na.rm = T)

#From the mean of average rating, it can be observed that the books that fall under the 'huge' 
#category have the highest average rating compared to all other categories  

#From the mean of text reviews count, it can be observed that the books that fall under the 'large' 
#category have the highest reviews count compared to all other categories.

#The average publication year shows 'huge' books were published in the early 2000's.
#Trends probably changed towards Medium sized books around 2008's.

```

### Question 4
```{r}
#Using lapply to perform same function as we did in part - 3
books_by_size <- split(data.frame(books$average_rating, books$text_reviews_count, books$publication_year), book_size)
lapply(books_by_size, colMeans, na.rm=T)

#Class
class(books_by_size)
```

###Question 5
```{r}
en_books <- books[books$language_code %in% c("en-US", "en-CA", "en-GB", "eng", "en", "en-IN") & books$publication_year > 2000, c("author_id", "book_id", "average_rating", "description", "title", "ratings_count", "language_code", "publication_year")]
res <- subset(books, subset=(language_code %in% c("en-US", "en-CA", "en-GB", "eng", "en", "en-IN")) & (publication_year > 2000), select=c("author_id", "book_id", "average_rating", "description", "title", "ratings_count", "language_code", "publication_year") )
dim(en_books)  #325499 X 8
dim(res)       #243269 X 8

#Answer why dimension is different 
#The dimensions are different because the en_books comprises of NA values which can be checked using the is.na() function.
#These NA values arent included on the creation of the dataframe 'res' using the subset command. This is because the subset 
#command inherently eliminates the NA values from the newly created dataframe. 

```
###Question 6
```{r}
mymergedDF <- merge(res, authors, by="author_id")
dim(mymergedDF)
```

###Question 7
```{r}
df <- mymergedDF[mymergedDF$name == 'Bill Bryson',]
head(df)
dim(df) #43x12
max(df$average_rating.x) #For the books 
df[which.max(df$average_rating.x),]$title

#I agree with "A Really Short History of Nearly Everything" to be the highest rated
#book written by Bill Bryson as it demonstrated to have the highest average rating of 4.22. 
#It stood up because of its rating out of all the 43 books by the author 
```

Submitting deliverables: project07.RMD, project07.R and project07.pdf

## Pledge
By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
