---
title: "Project 4 Solutions"
output:
  pdf_document: default
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## (Abhimanyu Agarwal)

## Collaborators: N/A
## TA help: 
## 1) Hilda Ibriga : Helped me with Question 5
## Online resources used: N/A 

### Question 1
```{r}
### Question 1
#Loads into dataframe called "splash_mountain" using read.csv()
splash_mountain <- read.csv("/class/datamine/data/disney/splash_mountain.csv")

#Mean using loop along with conditionals
counter <- 0                                   #Counter variable
sum <- 0
for(i in splash_mountain$SPOSTMIN)             #Enters the for loop, iterates over SPOSTMIN column 
  {
  if(is.na(i) != TRUE )                        #Makes sure NA values arent included in the mean sum
    {
    if( i != -999)                             #Makes sure -999 values arent included in the mean sum 
      {
      sum <- sum + i                           #Add values one by one to the sum
      counter <- counter + 1                   #Counter variable increments by 1
      }
    }
  }
mean <- sum/counter                            #Computes the mean as shown by the division
head(mean)                                     #Prints the mean value
```

### Question 2
```{r}
#Loads into dataframe called "flight_of_passage" using read.csv()
ride_name <- read.csv("/class/datamine/data/disney/flight_of_passage.csv")
for (i in 1:nrow(ride_name))                                            #Enters the for loop, iterates over every row value          
  {
  if(any(ride_name[i, c("SPOSTMIN", "SACTMIN")] == -999, na.rm = TRUE)) #Checks conditions to classify based on which value is -999
    {
      ride_name$status[i] = "closed"                                    #Assign the status "closed" if value is -999
    }
  else
    {
      ride_name$status[i] = "open"                                      #Assign the status "open" if value is not -999
    }
  }
ride_name$status = factor(ride_name$status)                             #After exiting the loop, it changes it into factor

#Printing str result
str(ride_name)
table(ride_name$status)                                                 #Prints the number of open and closed status indicators 
```

### Question 3
```{r}
#Assigns status open
status <- rep("open", times = nrow(ride_name))

#Applies conditionals and assigns "closed" status
status[which((ride_name$SPOSTMIN) == -999 | (ride_name$SACTMIN == -999))] <- "closed" 

#After checking the conditionals, it changes it into factor 
ride_name$status <- factor(status)

#Displays the entire dataframe, you could check the new status
head(ride_name)

#Printing str result
str(ride_name)
table(ride_name$status)
```

### Question 4
```{r}
#Using table to get a count of "closed" and "open" status
#Loads into dataframe called "splash_mountain" using read.csv()
splash_mountain <- read.csv("/class/datamine/data/disney/splash_mountain.csv")

#Assigns status open
status <- rep("open", times = nrow(splash_mountain))

#Applies conditionals and assigns "closed" status
status[which((splash_mountain$SPOSTMIN) == -999 | (splash_mountain$SACTMIN == -999))] <- "closed" 

#After checking the conditionals, it changes it into factor 
splash_mountain$status <- factor(status)

pie(table(splash_mountain$status), col = c("#8E6F3E", "#1c5253"), main = "Updated Status for Splash Mountain")    
#Obtain closed vs open categorical values 
#plot the data into pie chart
```

###Question 5
```{r}
ride_names <- c("splash_mountain", "soarin", "pirates_of_caribbean", "expedition_everest", "flight_of_passage", "rock_n_rollercoaster")
ride_files <- paste0(c("/class/datamine/data/disney/"), ride_names, ".csv")

mypiechart <- function(x){

#Saving it into a "ride file" dataframe
  ride_file <- read.csv(paste0(c("/class/datamine/data/disney/"), x, ".csv"))

#Assigns status open
  ride_file$status <- "open"
  
#Applies conditionals and assigns "closed" status 
  ride_file$status[which(ride_file$SPOSTMIN == -999 | ride_file$SACTMIN == -999)] <- "closed" 

#After checking the conditionals, it changes it into factor  
  ride_file$status = factor(ride_file$status)                            
  
#Pie chart and its formatting 
  pie(table(ride_file$status), col = c("#8E6F3E", "#1c5253"), main = x)    
}

par(mfrow=c(2,3))
for (i in ride_names)
  {
  mypiechart(i)
  }

```
Submitting deliverables: project04.RMD, project04.R and project04.pdf

## Pledge
By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
