---
title: "Project 1 Solutions"
output:
  pdf_document: default
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## (Abhimanyu Agarwal)

## Collaborators: N/A
## TA help: 
## 1) Kim, Question 6, Helped me in understanding the paste() in R.
## 2) Hanwen Gu, Question 6, Helped me re-structure my answer to demonstrate understanding.
## Online resources used: N/A 

### Question 1

The memory on the 7 frontend nodes is: 4 * 512 + 3 * 768 = 4352 GB = 4.3 TB and 4 * 20 + 3 * 20 = 140 cores. 

The memory on the 28 nodes in the sub-cluster is: 24 * 64 + 4 * 192 = 2304 GB = 2.3 TB and 24 * 20 + 4 * 16 = 544 cores.

The memory on Abhimanyu's laptop is 8 GB and 4 cores.

### Question 2

The node we are working on is:

```{r}
system("hostname", intern=T)
```
We are working on Scholar front end number 03. 

### Question 3

Printed Message Sentence: "You've successfully loaded The Data Mine R settings!"

### Question 4

There are 3 chunks of R code, 1 chunk of Python, 1 chunk of Bash and 1 chunk of SQL.

### Question 5

Basically 1,2 and 3 are stored into a variable called "my_variable".

```{r}
my_variable <- c(1,2,3)
my_variable
```

The displayed output is: 1 2 3

### Question 6

Referring back to question 1, we can perform the following arithmetic calculations: 

Memory (GB) and Core (Number of Core units) calculations using R for 7 front end respectively:
```{r}
4 * 512 + 3 * 768
4 * 20 + 3 * 20

```

Memory (GB) and Core (Number of Core units) calculations using R for 28 sub-clusters respectively:
```{r}
24 * 64 + 4 * 192 
24 * 20 + 4 * 16
```

### Question 7

We load in given dataset as follows:

```{r}
dat <- read.csv("/class/datamine/data/disney/splash_mountain.csv")
head(dat)
```

### Question 8

Submitting deliverable: project01.RMD, project01.R and project01.pdf

## Pledge

By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
